`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-07 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
plot styling updates

umap_theme <- list(
  coord_fixed(),
  theme_classic(),
  theme(
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    legend.position = "bottom"
  )
)
```

@@

```{r, fig.height = 8}
# Filter to just cells in the library to avoid warnings
library_has_cnv_df <- has_cnv_df |>
  dplyr::filter(library_id == params$library_id)

celltype_umap <- ggplot(library_has_cnv_df) +
  aes(x = UMAP1, y = UMAP2, color = celltype_n) +
  geom_point(size = 0.25, alpha = 0.4) +
  guides(color = guide_legend(override.aes = list(size = 2, alpha = 1))) +
  labs(title = "Cell types") +
  umap_theme

cnv_umap <- ggplot(library_has_cnv_df) +
  aes(x = UMAP1, y = UMAP2, color = total_cnv_per_cell) +
  geom_point(size = 0.25, alpha = 0.4) +
  scale_color_viridis_c() +
  labs(title = "Total CNV per cell") +
  umap_theme

@@

# 11 hex colors!
# adapted from 'Classic 10' from paletteer: https://r-graph-gallery.com/color-palette-finder
colors <- c("#1F77B4", "#FF7F0E", "#2CA02C", "#D6272F", "#9467BD", "#8C564B", "#E377C2", "#7F7F7F", "#BCBD22", "#17CFFB", "#17CF1F")

ggplot(query_only_df) +
  aes(
    x = forcats::fct_infreq(subcluster),
    fill = celltype_fine_n
  ) +
  geom_bar() +
  scale_fill_manual(values = colors) +
  theme(axis.text.x = element_blank())
```

>>>>

umap_theme <- list(
  coord_fixed(),
  theme_classic(),
  theme(
    axis.ticks = element_blank(),
    axis.text = element_blank()
  )
)
```

@@

```{r, fig.width = 12}
# Filter to just cells in the library to avoid warnings
library_has_cnv_df <- has_cnv_df |>
  dplyr::filter(library_id == params$library_id)

celltype_umap <- ggplot(library_has_cnv_df) +
  aes(x = UMAP1, y = UMAP2, color = celltype_n) +
  geom_point(size = 0.2, alpha = 0.3) +
  guides(color = guide_legend(override.aes = list(size = 2, alpha = 1))) +
  labs(title = "Cell types") +
  umap_theme

cnv_umap <- ggplot(library_has_cnv_df) +
  aes(x = UMAP1, y = UMAP2, color = total_cnv_per_cell) +
  geom_point(size = 0.2, alpha = 0.3) +
  scale_color_viridis_c() +
  labs(title = "Total CNV per cell") +
  umap_theme

@@

# 11 hex colors!
# adapted from 'Classic 10' from paletteer: https://r-graph-gallery.com/color-palette-finder
colors <- c("#1F77B4", "#FF7F0E", "#2CA02C", "#D6272F", "#9467BD", "#8C564B", "#E377C2", "#7F7F7F", "#BCBD22", "#17CFFB", "#17CF1F")
```

```{r, fig.width = 12}
ggplot(query_only_df) +
  aes(
    x = forcats::fct_infreq(subcluster),
    fill = celltype_fine_n
  ) +
  geom_bar() +
  scale_fill_manual(values = colors) +
  theme(axis.text.x = element_blank())
```
